### 2020-01-07 report/02-methods.Rmd
SEM with 8 pca axis: 2 * (median/cv) * (press/evt)

habitat_station %<>%
  left_join(left_join(flow_temp_med, flow_temp_cv, by = "station"), by = "station")
habitat_pressure <- habitat_station
mysave(habitat_pressure, dir = mypath("report"), overwrite = TRUE)
```

@@

@@

```{r dist-env, fig.cap = "Histogram of the station average environmental values through time."}

dist_env <- habitat_pressure %>%
  select(station, width_river_mean:temperature_cv) %>%
  gather(env_var, value, width_river_mean:temperature_cv) 
med_dist_env <- dist_env %>%
  group_by(env_var) %>%
  summarise(value = median(value, na.rm = TRUE))

@@

```{r split-rivers, fig.dim = c(7, 12)}
hab_type <- habitat_pressure %>%
  mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
  wide_bin = ifelse(width_river_mean > median(width_river_mean), TRUE, FALSE),
  hab_type = map2_chr(high_bin, wide_bin, function(high, wide){
    if (high) {
      if (wide) {
	"high_wide"
      } else {
	"high_narrow"
      }
    } else {
      if (wide) {
	"low_wide"
      } else {
	"low_narrow"
      }
    }

@@

```{r}
com <- ungroup(community_analysis) %>%
  select(opcod, species, biomass) %>%
  spread(species, biomass) %>%
  left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  filter(!is.na(station)) %>%
  mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
  select(-opcod) %>%
  group_by(station) %>%
  summarise_all(list(median))

com_mat <- as.matrix(com[, names(com) != "station"])
rownames(com_mat)  <- com$station

order_st <- match(temporal_community_metrics$station, com$station) 
tps_com_met <- temporal_community_metrics[order(order_st),]

@@

nmds <- metaMDS(com_mat, k=3, trymax = 100)
stressplot(nmds)
plot(nmds)
mysave(nmds, dir = mypath("report"), overwrite = TRUE)

bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
orditorp(nmds, display="sites",
  col= bluefunc(15)[findInterval(tps_com_met$richness_avg, seq(1,15))],
   cex = findInterval(log10(tps_com_met$biomass_med), seq(1, 4, 1))/2,
  air=0.01, pch = "+", labels = "+")

```{r}
# Add habitat
match_st <- match(habitat_pressure$station, com$station)
habitat <- habitat_pressure[order(match_st), ]
match_st_com <- match(temporal_community_metrics$station, com$station)
com_metrics <- temporal_community_metrics[order(match_st_com), ]
```

@@

```{r basin-st}
station_analysis <- get_basin_station(sf_obj = TRUE)
plot(station_analysis[,"basin"])
# How many station by basin:
nb_st_basin <- station_analysis %>%
  group_by(basin) %>%
  summarise(nobs = n())
```

```{r basin-com}
dev.off()
match_st_basin <- match(station_analysis$station, com$station)
st_basin <- station_analysis[order(match_st_basin), ] %>%
  mutate(basin = ifelse(is.na(basin), "INCONNU", basin))

@@

```{r}
match_st <- match(hab_type$station, com$station)
hab_type <- hab_type[order(match_st), ]
ordiplot(nmds,type="points", choices = c(1, 2))
orditorp(nmds,display="species",col="red",air=0.01)
u_hab  <- unique(hab_type[["hab_type"]])
for (i in seq_along(u_hab)) {
  ordihull(nmds, groups = hab_type[["hab_type"]], alpha = .1,
 show.group = u_hab[i], col = i, draw = 'polygon', label = T)
}
```

>>>>

habitat_station %<>%
  left_join(left_join(flow_temp_med, flow_temp_cv, by = "station"), by = "station") %>%
  filter(station %in% op_analysis$station)
habitat_pressure <- habitat_station
```

@@

####

```{r pca-evt-press-med-cv}
evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler")
evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
  "avg_depth_station_cv")

press_var_cv <- c("fungicides_cv", "herbicides_cv", "insecticides_cv", "DBO_cv")
press_var_med <- c("fungicides_med", "herbicides_med",
  "insecticides_med","DBO_med")

#, "nitrates_med", "phosphore_med","nitrates_cv", "phosphore_cv", "DBO_cv"
hab_evt <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean,
  evt_var_cv)]
hab_press <- habitat_pressure[, names(habitat_pressure) %in% c(press_var_med,
  press_var_cv)]

p_pca_clim_phy_press <- map2(
  list(hab_evt, hab_press),
  c("EVT", "Pressure"),
  plot_pca)
plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
```

####

```{r}
hab_mean <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean , press_var_med)]
hab_cv <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_cv, press_var_cv)]

p_pca_clim_phy_press <- map2(
  list(hab_mean, hab_cv),
  c("Med", "Cv"),
  plot_pca)
plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
```

####

```{r}
pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean, evt_var_cv, press_var_med, press_var_cv, "station")] %>% 
  na.omit
hab_evt_mean <- pca_pressure[, names(pca_pressure) %in% evt_var_mean]
hab_evt_cv <- pca_pressure[, names(pca_pressure) %in% evt_var_cv]
hab_press_mean <- pca_pressure[, names(pca_pressure) %in% press_var_med]
hab_press_cv <- pca_pressure[, names(pca_pressure) %in% press_var_cv]

p_pca_clim_phy_press <- map2(
  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
  c("Med evt", "Cv evt", "Med press", "Cv press"),
  plot_pca)
plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
```

```{r}
pca_clim_phy_press <- map(
  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
  function(.data) dudi.pca(as.data.frame(na.omit(.data)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE))

names(pca_clim_phy_press) <- c("med_evt", "cv_evt", "med_press", "cv_press")
```

#### Rotate PCA axis

```{r}
pca_rotated <- map2( 
  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
  c("Med evt", "Cv evt", "Med press", "Cv press"),
  function(.data, title) {
    .data %<>% na.omit
    pca <- dudi.pca(as.data.frame(.data), scannf = FALSE, nf = 2, center = TRUE, scale = TRUE)
    pca_rotated <- psych::principal(.data, rotate="varimax", nfactors=2,
      scores=TRUE)

    return(list(normal = pca, rotated = pca_rotated))

  })
names(pca_rotated) <- c("med_evt", "cv_evt", "med_press", "cv_press")

test <- vector(mode = "list", length = 4)
for (i in seq_along(names(pca_rotated))) {

  s.corcircle(
    pca_rotated[[i]]$rotated$loadings[1:nrow(pca_rotated[[i]]$rotated$loadings),], xax = 1,
    yax = 2)
  rotated_plot <- recordPlot()

   pca_plot <- fviz_pca_var(pca_rotated[[i]]$normal,
      axes = c(1, 2),
      col.var = "contrib", # Color by contributions to the PC
      gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
      repel = TRUE # Avoid text overlapping
    )

  test[[i]] <- plot_grid(rotated_plot, pca_plot)
  rm(rotated_plot)

}
plot_grid(plotlist=test)
mysave(pca_rotated, dir = mypath("report"), overwrite = TRUE)
```

```{r add pca axis to habitat pressure}

test <- map(pca_rotated, function(.pca) .pca$rotated$scores)
axis_names <- paste0(rep(names(pca_rotated), each = 2), c("1", "2"))
test2 <- do.call(cbind, test)
colnames(test2) <- axis_names
rotated_axis_st <- cbind(pca_pressure[, "station"], test2)

habitat_pressure %<>%
  left_join(rotated_axis_st, by = "station")

mysave(habitat_pressure, dir = mypath("report"), overwrite = TRUE)
```

@@

```{r dist-env, fig.cap = "Histogram of the station average environmental values through time."}
dist_env <- habitat_pressure %>%
  select(station, width_river_mean:temperature_cv) %>%
  gather(env_var, value, width_river_mean:temperature_cv) 
med_dist_env <- dist_env %>%
  group_by(env_var) %>%
  summarise(value = median(value, na.rm = TRUE))

@@

```{r split-rivers, fig.dim = c(7, 12)}
hab_type <- habitat_pressure %>%
  filter(station %in% op_analysis$station) %>%
  mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
  wide_bin = ifelse(width_river_mean > median(width_river_mean), TRUE, FALSE),
  hab_type = map2_chr(high_bin, wide_bin, function(high, wide){
    if (high) {
      if (wide) {
	"high_wide"
      } else {
	"high_narrow"
      }
    } else {
      if (wide) {
	"low_wide"
      } else {
	"low_narrow"
      }
    }

@@

@@

myload(nmds, com_mat, dir = mypath("report"))

stressplot(nmds)
plot(nmds)

order_st <- match(temporal_community_metrics$station, com_mat$station) 
tps_com_met <- temporal_community_metrics[order(order_st),]

bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
orditorp(nmds, display="sites",
  col= bluefunc(15)[findInterval(tps_com_met$richness_avg, seq(1,15))],
   cex = findInterval(log10(tps_com_met$biomass_med), seq(1, 4, 1))/2,
  air=0.01, pch = "+", labels = "+")
```

```{r}
# Add habitat
habitat_press  <- filter(habitat_pressure, station %in% com_mat$station)
match_st <- match(habitat_press$station, com_mat$station)
habitat <- habitat_press[order(match_st), ]
match_st_com <- match(temporal_community_metrics$station, com_mat$station)
com_metrics <- temporal_community_metrics[order(match_st_com), ]
```

@@

```{r basin-st}
station_analysis <- get_basin_station(sf_obj = TRUE) %>%
  filter(station %in% com_mat$station)

plot(station_analysis[,"basin"])
# How many station by basin:
nb_st_basin <- station_analysis %>%
  group_by(basin) %>%
  summarise(nobs = n())
```

```{r basin-com}
dev.off()
match_st_basin <- match(station_analysis$station, com_mat$station)
st_basin <- 
  station_analysis[order(match_st_basin), ] %>%
  mutate(basin = ifelse(is.na(basin), "INCONNU", basin))

@@

```{r}
match_st <- match(hab_type$station, com_mat$station)
hab_type <- hab_type[order(match_st), ]
ordiplot(nmds,type="points", choices = c(1, 2))
orditorp(nmds,display="species",col="red",air=0.01)
u_hab  <- unique(hab_type[["hab_type"]])
for (i in seq_along(u_hab)) {
  ordihull(nmds, groups = hab_type[["hab_type"]], alpha = .1,
 show.group = u_hab[i], col = i, draw = 'polygon', label = T)
}
```

### 2020-01-07 report/03-results.Rmd
Test w/wht ANG + statistical averaging
SEM with 8 pca axis: 2 * (median/cv) * (press/evt)

cor_avg <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med"))) %>%
  cor()
#knitr::kable(cor_avg)
as.data.frame(round(cor_avg,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
cor_cv <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("cv"))) %>%
  cor()
as.data.frame(round(cor_cv,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

>>>>

cor_avg <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med"))) %>%
  na.omit %>%
  cor(., method = "spearman")
#knitr::kable(cor_avg)
as.data.frame(round(cor_avg,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
cor_cv <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("cv"))) %>%
  na.omit %>%
  cor(., method = "spearman")

as.data.frame(round(cor_cv,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

### 2020-01-07 report/05-stability.Rmd
SEM with 8 pca axis: 2 * (median/cv) * (press/evt)

```{r}
myload(nmds, dir = mypath("report"))
lav_data <- compute_sem_dataset(
  com = temporal_community_metrics,
  network = temporal_network_metrics, 
  hab_press = habitat_pressure, 
  sync = synchrony,
  nmds = nmds,
  basin = st_basin 
  )
```

@@

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = nmds,
  basin = st_basin 
  )

>>>>

```{r}
myload(nmds, dir = mypath("report"))
lav_data <- compute_sem_dataset(
  com = temporal_community_metrics,
  network = temporal_network_metrics, 
  hab_press = habitat_pressure, 
  sync = synchrony,
  nmds = NULL,
  basin = st_basin 
  )
```

@@

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )
